Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2018-12-10 analysis/paper/paper.Rmd
Added libraries to paper.RMD. Also made all script files run internally (look around line 260 in paper for calls to both data_exploration and units_species, the problematic ones). However, I still can't knit the doc because of some sort of working directory problem, so run into an error at the CSV script. If the directory isn't giving you a problem it should knit.
i have changed the knitting settings to put the paper in the project directory instead of the /paper folder. Now the codes for scripts run!

library(dplyr);library(ggplot2);library(dbplyr);library(readr)

@@

#NOTE: working directory when knitting markup is /analysis/paper. So relative pathway needs to be ../scripts etc.

source("../scripts/data_retrievalCSVs.R")

```

@@

```{r}
source("../scripts/data_exploration.R")
```

@@

```{r}
# what commit is this file at? You may need to change the path value
# if your Rmd is not in analysis/paper/
git2r::repository("../..")
```

>>>>

library(dplyr);library(ggplot2);library(dbplyr);library(readr);library(stringr);library(tidyr);library(lubridate);library(ggthemes);library(ggforce)

@@

#NOTE: working directory when knitting markup is /analysis/paper. So relative pathway needs to be ../scripts etc.
getwd()
source("./analysis/scripts/data_retrievalCSVs.R")
```

@@

```{r, eval=TRUE}
source("./analysis/scripts/data_exploration.R")
#source("../scripts/units_species.R")
```

@@

```{r}
# what commit is this file at? You may need to change the path value
# if your Rmd is not in analysis/paper/
#git2r::repository("../..")
```
